Deuteron Electro-Disintegration at Very High Missing Momenta

### 2020-07-27 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/authorlist-rev.tex
added directory with final PRL draft

%Author List from Spring 2018 Hall C Commissioning + SIDIS Runs
%Comment / Uncomment accordingly
\author{C.~Yero$^{1}$}       %Main author for E12-10-003 experiment
\author{D.~Abrams$^{2}$}           %Commissioning ONLY
\author{Z.~Ahmed$^{3}$}            %Commissioning ONLY
\author{A.~Ahmidouch$^{4}$}        % . . .----> HOLLY
\author{B.~Aljawrneh$^{4}$}        %Commissioning ONLY
\author{S.~Alsalmi$^{5}$}          %Commissioning ONLY
\author{R.~Ambrose$^{3}$}          %Commissioning + SIDIS
%\author{D.~Androic}         %Color Transparency ONLY

@@

\author{M.~Bukhari$^{14}$}          %Commissioning ONLY

@@

\author{M.~Dlamini$^{16}$}          %Commissioning ONLY
\author{J.~Dunne$^{8}$}            %Commissioning ONLY
\author{B.~Duran$^{6}$}            %Commissioning + SIDIS

@@

\author{E.~Fuchey$^{17}$}           %Commissioning ONLY

@@

\author{F.A.~Gonzalez$^{18}$}       %Commissioning + SIDIS
\author{O.~Hansen$^{15}$}           %Commissioning ONLY
\author{F.~Hauenstein$^{19}$}       %Commissioning ONLY

@@

\author{P.~King$^{16}$}             %Commissioning ONLY
\author{E.~Kinney$^{20}$}           %Commissioning ONLY (SIDIS Co-Spokesperson)

@@

\author{S.~Li$^{21}$}               %Commissioning ONLY

@@

\author{G.~Niculescu$^{22}$}        %Took 11 shifts (Why is NOT included in Holly's list) ??????
\author{M.~Niculescu$^{22}$}        %Took 11 shifts (Why is NOT included in Holly's list) ??????

@@

\author{N.~Nuruzzaman$^{23}$}       %Commissioning ONLY

@@

\author{S.~Park$^{18}$}             %Commissioning + SIDIS

@@

\author{M.~Rehfuss$^{6}$}          %Commissioning ONLY

@@

\author{A.~Sun$^{24}$}               %Commissioning + SIDIS

@@

\author{J.~Zhang$^{18}$}        %Commissioning ONLY 

@@

\affiliation{$^{1}$Florida International University, University Park, Florida 33199, USA}
\affiliation{$^{2}$University of Virginia, Charlottesville, Virginia 22903, USA}
\affiliation{$^{3}$University of Regina, Regina, Saskatchewan S4S 0A2, Canada}
\affiliation{$^{4}$North Carolina Agricultural and Technical State University, Greensboro, North Carolina 27411, USA}
\affiliation{$^{5}$Kent State University, Kent, Ohio 44240, USA}
\affiliation{$^{6}$Temple University, Philadelphia, Pennsylvania 19122, USA}
\affiliation{$^{7}$A.I. Alikhanyan National Science Laboratory (Yerevan Physics Institute), 2 Alikhanian Brothers Street, 0036, Yerevan, Armenia}
\affiliation{$^{8}$Mississippi State University, Mississippi State, Mississippi 39762, USA}
\affiliation{$^{9}$The College of William \& Mary, Williamsburg, Virginia 23185, USA}
\affiliation{$^{10}$University of Tennessee, Knoxville, Tennessee 37996, USA}
\affiliation{$^{11}$Catholic University of America, Washington, DC 20064, USA}
\affiliation{$^{12}$Hampton University, Hampton, Virginia 23669, USA}
\affiliation{$^{13}$Christopher Newport University, Newport News, Virginia 23606, USA}
\affiliation{$^{14}$Jazan University, Jazan 45142, Saudi Arabia}
\affiliation{$^{15}$Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606, USA}
\affiliation{$^{16}$Ohio University, Athens, Ohio 45701, USA}
\affiliation{$^{17}$University of Connecticut, Storrs, Connecticut 06269, USA}
\affiliation{$^{18}$Stony Brook University, Stony Brook, New York 11794, USA}
\affiliation{$^{19}$Old Dominion University, Norfolk, Virginia 23529, USA}
\affiliation{$^{20}$University of Colorado Boulder, Boulder, Colorado 80309, USA}
\affiliation{$^{21}$University of New Hampshire, Durham, New Hampshire 03824, USA}
\affiliation{$^{22}$James Madison University, Harrisonburg, Virginia 22807, USA}
\affiliation{$^{23}$Rutgers University, New Brunswick, New Jersey 08854, USA}
\affiliation{$^{24}$Carnegie Mellon University, Pittsburgh, Pennsylvania 15213, USA}

>>>>

%Author List from Spring 2018 Hall C Commissioning + SIDIS Runs
%Comment / Uncomment accordingly
\author{C.~Yero$^{1}$}       %Main author for E12-10-003 experiment
\author{D.~Abrams$^{2}$}           %Commissioning ONLY
\author{Z.~Ahmed$^{3}$}            %Commissioning ONLY
\author{A.~Ahmidouch$^{4}$}        % . . .----> HOLLY
\author{B.~Aljawrneh$^{4}$}        %Commissioning ONLY
\author{S.~Alsalmi$^{5}$}          %Commissioning ONLY
\author{R.~Ambrose$^{3}$}          %Commissioning + SIDIS
%\author{D.~Androic}         %Color Transparency ONLY

@@

\author{M.H.S.~Bukhari$^{14}$}          %Commissioning ONLY

@@

\author{M.~Dlamini$^{17}$}          %Commissioning ONLY
\author{J.~Dunne$^{8}$}
%Commissioning ONLY
\author{B.~Duran$^{16}$}            %Commissioning + SIDIS

@@

\author{E.~Fuchey$^{18}$}           %Commissioning ONLY

@@

\author{F.A.~Gonzalez$^{19}$}       %Commissioning + SIDIS
\author{J.O.~Hansen$^{15}$}           %Commissioning ONLY
\author{F.~Hauenstein$^{20}$}       %Commissioning ONLY

@@

\author{P.~King$^{17}$}             %Commissioning ONLY
\author{E.~Kinney$^{21}$}           %Commissioning ONLY (SIDIS Co-Spokesperson)

@@

\author{S.~Li$^{22}$}               %Commissioning ONLY

@@

\author{G.~Niculescu$^{23}$}        %Took 11 shifts (Why is NOT included in Holly's list) ??????
\author{M.~Niculescu$^{23}$}        %Took 11 shifts (Why is NOT included in Holly's list) ??????

@@

\author{N.~Nuruzzaman$^{24}$}       %Commissioning ONLY

@@

\author{S.~Park$^{19}$}             %Commissioning + SIDIS

@@

\author{M.~Rehfuss$^{16}$}          %Commissioning ONLY

@@

\author{A.~Sun$^{25}$}               %Commissioning + SIDIS

@@

\author{J.~Zhang$^{19}$}        %Commissioning ONLY 

@@

\affiliation{$^{1}$Florida International University, University Park, Florida 33199, USA}
\affiliation{$^{2}$University of Virginia, Charlottesville, Virginia 22903, USA}
\affiliation{$^{3}$University of Regina, Regina, Saskatchewan S4S 0A2, Canada}
\affiliation{$^{4}$North Carolina Agricultural and Technical State University, Greensboro, North Carolina 27411, USA}
\affiliation{$^{5}$Kent State University, Kent, Ohio 44240, USA}
\affiliation{$^{6}$Argonne National Laboratory, Lemont, Illinois 60439, USA}   %fixed address for Whit and Sylvester
\affiliation{$^{7}$A.I. Alikhanyan National Science Laboratory (Yerevan Physics Institute), 2 Alikhanian Brothers Street, 0036, Yerevan, Armenia}
\affiliation{$^{8}$Mississippi State University, Mississippi State, Mississippi 39762, USA}
\affiliation{$^{9}$The College of William \& Mary, Williamsburg, Virginia 23185, USA}
\affiliation{$^{10}$University of Tennessee, Knoxville, Tennessee 37996, USA}
\affiliation{$^{11}$Catholic University of America, Washington, DC 20064, USA}
\affiliation{$^{12}$Hampton University, Hampton, Virginia 23669, USA}
\affiliation{$^{13}$Christopher Newport University, Newport News, Virginia 23606, USA}
\affiliation{$^{14}$Jazan University, Jazan 45142, Saudi Arabia}
\affiliation{$^{15}$Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606, USA}
\affiliation{$^{16}$Temple University, Philadelphia, Pennsylvania 19122, USA}
\affiliation{$^{17}$Ohio University, Athens, Ohio 45701, USA}
\affiliation{$^{18}$University of Connecticut, Storrs, Connecticut 06269, USA}
\affiliation{$^{19}$Stony Brook University, Stony Brook, New York 11794, USA}
\affiliation{$^{20}$Old Dominion University, Norfolk, Virginia 23529, USA}
\affiliation{$^{21}$University of Colorado Boulder, Boulder, Colorado 80309, USA}
\affiliation{$^{22}$University of New Hampshire, Durham, New Hampshire 03824, USA}
\affiliation{$^{23}$James Madison University, Harrisonburg, Virginia 22807, USA}
\affiliation{$^{24}$Rutgers University, New Brunswick, New Jersey 08854, USA}
\affiliation{$^{25}$Carnegie Mellon University, Pittsburgh, Pennsylvania 15213, USA}

### 2020-07-27 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/body-rev.tex
added directory with final PRL draft

For each spectrometer, a logical signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\

@@

which require comparatively few parameters while still producing a high-precision fit to the NN scattering data.

>>>>

For each spectrometer, a logic signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\

@@

which requires comparatively few parameters while still producing a high-precision fit to the NN scattering data.

### 2020-07-27 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/introduction-diff.tex
added directory with final PRL draft

\indent At large $Q^{2}$, FSI are described by the General Eikonal Approximation (GEA) \cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015}, which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.

>>>>

\indent At large $Q^{2}$, FSI can be described by the Generalized Eikonal Approximation (GEA) \cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015}, which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.

### 2020-07-27 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/prl-rev.tex
added directory with final PRL draft

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 05 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by June 01, 2020}
\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

\begin{abstract}
  $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
  over a range of neutron recoil momenta, $p_{\mathrm{r}}$, with $p_{\mathrm{r}}$ reaching up to $\sim1.0$ GeV/c. The data have
  been obtained at fixed neutron recoil angles $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
  transfer $\vec q$. The new data agrees well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$
  and $45^\circ$, final state interactions (FSI), meson exchange currents (MEC) and isobar configurations (IC) are suppressed and
  the plane wave impulse approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent
  theoretical calculations, where a significant disagreement for missing momenta $p_{\mathrm{r}}>700$ MeV/c is observed. 
\end{abstract}

>>>>

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 05 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by July 31, 2020}
\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

\begin{abstract}
  $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
  over a range of neutron recoil momenta, $p_{\mathrm{r}}$, with $p_{\mathrm{r}}$ reaching up to $\sim1.0$ GeV/c. The data have
  been obtained at fixed neutron recoil angles $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
  transfer $\vec q$. The new data agree well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$
  and $45^\circ$, final state interactions (FSI), meson exchange currents (MEC) and isobar configurations (IC) are suppressed and
  the plane wave impulse approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent
  theoretical calculations, where we observe a significant discrepancy for missing momenta $p_{\mathrm{r}}>700$ MeV/c. 
\end{abstract}

### 2020-07-27 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/body.tex
added directory with final PRL draft

For each spectrometer, a logical signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\

@@

measured in this experiment. As a result, most of the virtual photon momentum is transferred to the proton, which scatters at angles relative to $\vec{q}$ in the range $0.4^{\circ}\lesssim \theta_{pq}\lesssim21.4^{\circ}$.

@@

\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$,
and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the

@@

determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each missing momentum setting, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins. 

@@

over the kinematic bin. The systematic uncertainty associated with the radiative and bin-centering corrections was investigated using the Laget PWIA and 

@@

\noindent FSI models but negligible effects on the cross sections were found. The experimental and theoretical reduced cross sections were extracted and are defined as follows:

@@

$p_{\mathrm{r}}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$. For the two highest momentum settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$ . The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square). The good agreement between the Hall A and C data at lower $p_{\mathrm{r}}$

@@

for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.\\
\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq250$ MeV/c, the cross sections are well reproduced by all models when FSI are included.
The agreement at $p_{\mathrm{r}}\leq250$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)

@@

\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
AV18 models increasingly differ from the CD-Bonn calculation. In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c. The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.  In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c (Fig. \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig. \hyperref[fig:fig1]{1(b)}).\\
\indent The difference between the deuteron wave functions with CD-Bonn and Paris/AV18 potentials is 
how the NN potential is modeled based on the empirical NN scattering data.
The CD-Bonn model is based on the One-Boson-Exchange approach in which the 
nucleon-meson-meson couplings are constrained to describe the NN scattering phase shifts
extracted from the data. The interaction potential represents the static limit of 
this potential. Paris and AV18 potentials are phenomenological in which the 
Yukawa type interaction is introduced and parameters are fitted to describe the 
same NN scattering phase-shifts. The major difference between CD-Bonn and Paris/AV18 
potentials is that the former predicts much softer repulsive interaction at short distance which 
results in a smaller high momentum component in the deuteron wave function in momentum space.
%The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant
%(original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18
%groups to describe the NN potential.
The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\

@@

behavior (smaller fall-off) that overshadows any possibility of extracting the genuine momentum distributions.\\

@@

to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data confirm the Hall A approach of selecting a kinematic

@@

\indent At larger recoil momenta, where the ratio $R>1$ and increasing with $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ FSI start to dominate for

@@

\begin{figure}[!t]
\includegraphics[scale=0.5]{./prl_plots/PRL_plot2_WJC2.pdf}

@@

At $\theta_{nq}=45^{\circ}$, the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\

@@

At $p_{\mathrm{r}}>300$ MeV/c and $\theta_{nq}=75^{\circ}$, the data were statistically limited as our focus was on the smaller recoil angles. The Hall A data, however, shows a reasonable agreement with the FSI from all models which gives us confidence in our understanding

@@

\indent To summarize, this experiment extended the previous Hall A cross section measurements on the $^{2}\mathrm{H}(e,e'p)n$ reaction to 

@@

short range part of the deuteron wave function. The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data.

@@

At higher missing momenta ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data. 
Additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing
momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.\\

@@

to the equipment for the Hall C upgrade, making all four commissioning experiments possible. We would also like to
thank Misak Sargsian, Sabine Jeschonnek and J.W.Van Orden for providing the theoretical calculations as well as the useful
discussions we had on this topic. This work was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics

@@

under grant No. NRC-HQ-84-14-G-0040, the Doctoral Evidence Acquisition (DEA) Fellowship and the Natural Sciences and Engineering Research Council of Canada (NSERC).

>>>>

For each spectrometer, a logical hardware signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\

@@

measured in this experiment. As a result, most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$ in the range $0.4^{\circ}\lesssim \theta_{pq}\lesssim21.4^{\circ}$.

@@

\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$
and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$ where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the

@@

determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each missing momentum setting, and added in quadrature for overlapping pr bins. 

@@

over the kinematic bin. The systematic uncertainty associated with the radiative and bin-centering corrections was investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found.\\
\indent The experimental and theoretical reduced cross sections were extracted and are defined as follows:

@@

@@

$p_{\mathrm{r}}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$. For the two highest settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$ . The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square). The good agreement between the Hall A and C data at lower $p_{\mathrm{r}}$

@@

for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} and those for the Paris potential (blue) were by Laget \cite{LAGET2005}.\\
\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq300$ MeV/c, the cross sections are well reproduced  by  all models when FSI are included.
The agreement at $p_{\mathrm{r}}\leq300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)

@@

\indent Beyond $p_{\mathrm{r}}\sim300$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
AV18 models significantly differ from the CD-Bonn. In this region, the Paris/AV18 cross sections are dominated by the PWIA and within good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c. The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.  In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c (Fig. \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig. \hyperref[fig:fig1]{1(b)}).
The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant (original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18 groups
to describe the NN potential. The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\

@@

behaviour (smaller fall-off) that overshadows any possibility of extracting the momentum distributions.\\

@@

to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic

@@

\indent At larger recoil momenta, where the ratio is $R>1$ and increasing, for $\theta_{nq}=35^{\circ}$ FSI start to dominate for

@@

\begin{figure}[t!]
\includegraphics[scale=0.5]{./prl_plots/PRL_plot2.pdf}

@@

At $\theta_{nq}=45^{\circ}$ the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\

@@

At $p_{\mathrm{r}}>300$ MeV/c, the data were statistically limited as our focus was on the smaller recoil angles. The Hall A data, however, shows a reasonable agreement with the FSI from all models which gives us confidence in our understanding

@@

\indent This experiment extended the previous Hall A cross section measurements on the $^{2}\mathrm{H}(e,e'p)n$ reaction to 

@@

short range part of the deuteron wavefunction. The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data.

@@

At higher missing momenta, however, all models were unable to describe the data. \\
\indent In conclusion, additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing
momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.

@@

to the equipment for the Hall C upgrade, making all four commissioning experiments possible. This work
was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics

@@

under grant No. NRC-HQ-84-14-G-0040 and the Doctoral Evidence Acquisition (DEA) Fellowship.

### 2020-07-27 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/prl.tex
updated
added directory with final PRL draft

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 05 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by June 01, 2020}
\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

%\title{First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q$^{2}$}
%\title{$^{2}$H$(e,e'p)n$ Cross Section Measurements for Neutron Recoil Momenta up to $p_{r}\sim1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$}
%\title{Deuteron Electro-Disintegration up to $\sim$ 1 GeV/c Missing Momentum}
\title{Probing the Deuteron at Very Large Internal Momenta}

\input authorlist.tex

@@

\begin{abstract}
  $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
  over a range of neutron recoil momenta, $p_{\mathrm{r}}$, with $p_{\mathrm{r}}$ reaching up to $\sim1.0$ GeV/c. The data have
  been obtained at fixed neutron recoil angles $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
  transfer $\vec q$. The new data agrees well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$
  and $45^\circ$, final state interactions (FSI), meson exchange currents (MEC) and isobar configurations (IC) are suppressed and
  the plane wave impulse approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent
  theoretical calculations, where a significant disagreement for missing momenta $p_{\mathrm{r}}>700$ MeV/c is observed. 
\end{abstract}

>>>>

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 04 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by May 01, 2020}
\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

%\title{First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q$^{2}$}
%\title{$^{2}$H$(e,e'p)n$ Cross Section Measurements for Neutron Recoil Momenta up to $p_{r}\sim1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$}
\title{Deuteron Electro-Disintegration at Very High Missing Momenta}
\input authorlist.tex

@@

\begin{abstract}
$^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $-Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
reaching neutron recoil (missing) momenta up $p_{\mathrm{r}}\sim$ 1.0 GeV/c. The data have been obtained at fixed neutron recoil angles
$\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
transfer $\vec q$. The new data agrees well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$ and $45^\circ$, final state interactions (FSI),
meson exchange currents (MEC) and isobar configurations (IC) are
suppressed and the plane wave impulse approximation (PWIA) provides the
dominant cross section contribution. The new data are compared to recent
theoretical calculations, where a significant disagreement for
missing momenta $p_{\mathrm{r}}>700$ MeV/c has been observed. 
\end{abstract}
